---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Installation

```{r}
#install_github("zhamel/foo")
library(foo)
```

## Usage

This package consists of 4 functions which hopefully can make your life easier when dealing with factors.

### `fbind()`

**Goal**: Bind two factors together to get back a factor with the levels from both factors.

```{r}
fbind(iris$Species[c(1, 51, 101)], PlantGrowth$group[c(1, 11, 21)])
#> [1] setosa     versicolor virginica  ctrl       trt1       trt2      
#> Levels: ctrl setosa trt1 trt2 versicolor virginica
```

### `freq_out()`

**Goal**: Create a data frame consisting of the levels of the factor and its frequency.

```{r}
freq_out(iris$Species)
#> Source: local data frame [3 x 2]
#> 
#>            x     n
#>       (fctr) (int)
#> 1     setosa    50
#> 2 versicolor    50
#> 3  virginica    50
```

### `reorder_levels()`

**Goal**: Reordering the levels based on frequency (from least to most)

```{r}
reorder_levels(factor(c("a","a","b","c","c","c","c","d","d","d")))
#> [1] a b c d
#> Levels: c d a b
```

### `factor_to_char()`

**Goal**: Should your factor be a character instead? This function compares the length of the factor with the number of levels. If the length of the factor = # of levels of the factor, then `factor_to_char()` returns `TRUE`: maybe this shouldn't be a factor! Otherwise, if they are different, `factor_to_char()` returns `FALSE`: this time you may want to keep it as a factor!

```{r}
factor_to_char(iris$Species)
#>.[1] FALSE
```

